DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-04 paper/evaluation.tex
reorg: add comparison section

In comparison, NVIDIA's DAVE-2 system, which has the exact same neural
network architecture, is reportedly run at 30 Hz~\cite{Bojarski2016},
just a bit faster than the DeepPicar. Although we believe it was not
limited by their computing platform (we will experimentally compare
performance differences among multiple embedded computing platforms,
including NVIDIA's Jetson TK2, later in
Section~\ref{sec:eval-platforms}), the fact that the low-cost
Raspberry Pi 3 can achieve similar real-time control performance is
surprising.

@@

\subsection{Summary}
So far, we have systematically evaluated DeepPicar's real-time
characteristics from the perspective of end-to-end deep learning based
real-time control and made several observations.

First, we find that DeepPicar's computing platform,
the Raspberry Pi 3 Model B, offers adquate computing capacity to
to perform real-time control of the RC car at 20 Hz frequency (or
50ms per control loop). Given the complexity of the DNN we use, we are
pleasantly suprised by this finding. The time breakdown has shown that
the DNN inferencing operation, perforemd by the Tensorflow library, is
dominating the execution time, which is expected.

Second, we find that the scalability of Tensorflow's DNN inference 
implementation is not ideal: We find that using all four cores are 
only about 30\% better than using just a single core.

Third, we find that consolidating multiple DNN models---on different CPU
cores---is feasible based on the following two observations: (1)
DNN performance on a single is not much worse than on multicore; (2)
multiple DNN models running simultaneously do not cause severe
interference with each other.

Lastly, we however find that consolidating memory (DRAM) intensive
applications could jeopadize DNN performance because DNN performance
appear very sensitive to memory performance; we observe up to 9.6X
slowdown in DNN performance by co-scheduling synthetic memory
bandwidth intensive applications on idle cores.

@@

\subsection{Performance Requirements}
In the utilization of the Raspberry Pi 3 in our platform, there are a
few factors that need to be considered and/or enforced in order to
guarantee that the Pi is able to consistently perform at a desired
level. Specifically, these issues all have the potential to negatively
affect the cpu clock speed/frequency, which would result in decreased
performance. While, in the above experiments, the cpu operated at a
preferred clock speed of 1.2 GHz, it is entirely possible for the cpu
to operate at a lower frequency if the following problems are not
taken into account.

The most notable issue that can affect the cpu clock speed is that of
the power supplied to the Raspberry Pi. In essence, it is necessary
that the Pi be supplied with 2 Amps, as any less could hinder the Pi's
ability to maintain a 1.2 GHz frequency. In experiments conducted with
a power supply that only provided 1 Amp, the Pi was unable to sustain
a 1.2 GHz clock speed and, instead, fluctuated between operating at
600 MHz and 1.2 GHz. As a result, it is necessary, or at least highly
recommended, that the power supply used for the Raspberry Pi 3 be
capable of outputting 2 Amps, otherwise optimal performance isn't
guaranteed.  Another factor that can affect clock speed is that of the
cpu's temperature. Some model operations can be computationally
intensive, thus it is possible for the temperature of the cpu to
become relatively high. This can be especially problematic in
situations where multiple models are running  simultaneously on the
Pi. Consequently, thermal throttling may be used to decrease the clock
speed so that the cpu temperature stays at a safe level. Thus the
Raspberry Pi may not be suited for prolonged use, especially in cases
where the workload is relatively larger, such as running multiple
models. Rather, the Pi seems to be better suited for running in set
periods, after which it is turned  off or made idle so that the cpu is
allowed time to cool down.

\subsection{System Comparisons}
We compare the real time performance of the Raspberry Pi 3 to two other embedded computing platforms, 
the Intel UP Board the NVIDIA Tegra TX2, to evaluate their efficacy in vision-based autonomous 
vehicles. We conduct the same experiments done on the DeepPicar with each platform, and analyze the 
results.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/system_multicore}
  \caption{Inferencing time across platforms based on number of cores used.}
  \label{fig:sys_core}
\end{figure}

The results of the multicore tests can be seen in Figure~\ref{fig:sys_core}. It was found that the 
Intel UP Board performed better in all experiments. On average, it was able to perform inferencing 
operations, at least, twice as fast as the Raspberry Pi 3. As a result, the UP Board was able to 
satisfy the 50 ms WCET by a very clear margin (in the worst case, it would still meet it by $\sim$20 
ms), and, thus, demonstrates that it is more capable of autonomous driving than the Raspberry Pi 3.

The Intel UP Board also performed better in the multimodel tests, as is shown in 
Figure~\ref{fig:sys_model}. Once again, the UP was able to complete inferecing operations in half the 
time when compared to the Pi. Furthermore, the Intel UP Board was capable of satisfying the 50 ms 
WCET, while the Raspberry Pi 3 was unable to do so. As such, the Intel UP Board displays greater 
potential for the simultaneous execution of multiple models during self-driving operation, while the 
Raspberry Pi 3 would struggle to do so.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/system_multimodel}
  \caption{Inferencing time across platforms based on number of models run concurrently.}
  \label{fig:sys_model}
\end{figure}

Finally, we examined if the performance of the Intel UP Board and Tegra TX2 would be affected by the 
addition of the synthetic benchmarks. As summarized in Figure~\ref{fig;sys_bench}, the Intel UP Board 
did experience a change in its inferencing times, but the increase was not as drastic as is seen by 
the Raspberry Pi 3. in the worst case, the Intel UP Board produced times that were over two times as 
large, whereas the Raspberry Pi 3 output times that were around 10 times greater. The Intel UP Board 
was successful in completing inferencing operations in under 50 ms when benchmarks were run on a 
maximum of 2 cores, while the Raspberry Pi 3 failed to do so when any benchmark was introduced. As 
such, it can be concluded that the Intel UP Board would be more capable of running computationally 
heavy processes during autonomous driving, and that the Pi wouldn't be able to do the same.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/system_benchmark}
  \caption{Inferencing time across platforms based on number of cores used.}
  \label{fig:sys_bench}
\end{figure}

In the comparison of the real-time capabilities of three embedded computing platforms, we found that 
the Raspberry Pi 3 performed the worst. When compared to the Intel UP Board, inferencing on the Pi 
took twice as long across all multicore and multimodel experiments. The difference was even more 
noticeable in the the addition of computationally heavy synthetic benchmarks that had a much more 
dire effect on the Pi.

>>>>

In comparison, NVIDIA's DAVE-2 system, which has the exact same neural
network architecture, is reportedly run at 30 Hz~\cite{Bojarski2016},
just a bit faster than the DeepPicar. Although we believe it was not
limited by their computing platform (we will experimentally compare
performance differences among multiple embedded computing platforms,
including NVIDIA's Jetson TK2, later in
Section~\ref{sec:comparison}), the fact that the low-cost
Raspberry Pi 3 can achieve similar real-time control performance is
surprising.

@@

\subsection{Summary}
So far, we have evaluated DeepPicar's real-time
characteristics from the perspective of end-to-end deep learning based
real-time control, and made several observations.

First, we find that DeepPicar's computing platform,
the Raspberry Pi 3 Model B, offers adquate computing capacity to
perform real-time control of the RC car at 20 Hz frequency (or
50ms per control loop). Given the complexity of the DNN we use, we
were pleasantly suprised by this finding. The time breakdown shows that
the DNN inferencing operation, perforemd by the Tensorflow library,
dominates the execution time, which is expected.

Second, we find that scalability of Tensorflow's DNN inference 
implementation is limited: We find that using all four cores are 
only about 30\% better than using just a single core.

Third, we find that consolidating multiple DNN models---on different CPU
cores---is feasible as we find: (1) DNN performance using a single
core is not much worse than using multiple cores; (2) multiple DNN
models running simultaneously do not cause severe interference with
each other.

Lastly, we however find that consolidating memory (DRAM) performance
intensive applications could jeopadize DNN performance because DNN
performance appear very sensitive to memory performance; we observe up
to 9.6X slowdown in DNN performance by co-scheduling synthetic memory 
bandwidth intensive applications on idle cores.

@@
